Universal Anonymous Signatures

### 2022-08-12 prism-backend/research/gsac/relationships.tex
Updating proofs of UAS => MPS

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
          \nonumber \\
        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
          \pcreturn (0,\ast) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
        \nonumber   
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber \\
        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif \yeval^0 \neq 0:
          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn 0
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored).}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction is unforgeabile according to
  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
  \markulf{Hiding of $pk_U$?}
\end{theorem}

@@

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
ensures that opening outputs the evaluation of a PRF of the {\cid}s concatenated
with the verifier name; and (2) ensures that, if some {\cid} of the credentials
used to produce a signature have been added to a revocation list by the
verifier, the verifier will know it -- and hence will be able to reject the
signature. We first give a simple model in
\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
explicitly add
the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
credential used in a presentation transcript \utrans -- and which is essentially
equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
verifiable openings, but this would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

@@

\begin{theorem}[Issuance anonymity of \CUASRAC]
  \todo{review}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is one-way and collision-resistant, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
and $G=\finsp^\ast$. With these functions, the construction is essentially as in
\secref{ssec:related-models-gs}.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
is an input of \yinsp.

>>>>

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
          \nonumber \\
        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
          \pcreturn (0,\ast) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
          \nonumber \\
        & \feval^{g,MPS}(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif g(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},
          \msg) = 0: \pcreturn \bot \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\ast,g(\upk,\lbrace
          (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)) \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber \\
        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif \yeval^0 \neq 0:
          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn 0
          \nonumber \\
        & \finsp^{h,MPS}((\cdot,\yeval^1),\upk,\cid,\attrs,\cdot) \coloneqq
          \pcreturn h(\yeval^1,\upk,\cid,\attrs) \nonumber         
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means that the function fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{theorem}[Unforgeability of \CUASAC]
  \label{thm:forge-cuasac}
  If the base \CUASGen construction is unforgeabile according to
  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
  \markulf{Hiding of $pk_U$?}
\end{theorem}

@@

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
ensures that opening outputs the evaluation of a PRF of the {\cid}s concatenated
with the verifier name; and (2) ensures that, if some {\cid} of the credentials
used to produce a signature have been added to a revocation list by the
verifier, the verifier will know it -- and hence will be able to reject the
signature. We first give a simple model in
\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
explicitly add
the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans -- and
which is essentially equivalent to \Open in \UAS. For simplicity, we do not
include the equivalent to verifiable openings, but this would be
straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    In particular, this implies that it rejects queries for transcripts related
    to challenge users. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

@@

\begin{theorem}[Anonymity of \CUASRAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
  anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
  RAC scheme.
\end{theorem}

Note that, if we aim at global credential (resp. user) revocation rather than
verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
pair (resp., \upk), and no assumption regarding $F$ is needed.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
and $G=\finsp^\ast$. With these functions, the construction is direct.
\CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
pair by running \KeyGen and \ISet (with $\fissue^1$). For MPS's join, \CUASMPS
runs first \KeyGen to generate the user key pair, and then proceeds as in
\CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \yinsp.
